Pytorch-Bert-Text-Infilling

### 2020-10-26 scripts/model_starters/R/Pytorch-Bert-Text-Infilling.Rmd
rename function

```{r, warning=FALSE}
##### Prediction function
predict_tokens <- function(text_original) {
  ### Clean text
  text_stripped <- strip(text_original, char.keep = c("?", ".", "’", "~~"), digit.remove = TRUE, apostrophe.remove = FALSE,
                         lower.case = FALSE)
  ### Collect text errors
  errors <- hunspell(text_stripped)

@@

predict_tokens(text_original)
```

>>>>

```{r, warning=FALSE}
##### Prediction function
get_correct_text <- function(text_original) {
  ### Clean text
  text_stripped <- strip(text_original, char.keep = c("?", ".", "’", "~~"), digit.remove = TRUE, apostrophe.remove = FALSE,
                         lower.case = FALSE)
  ### Collect text errors
  errors <- hunspell(text_stripped)

@@

get_correct_text(text_original)
```
